---
title: "Favorite foods"
author: "Sophie Boyd"
date: "2-1-26"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(readxl)
```

# Part 1: Excel to CSV Workflow


## Step 1: Read the Data

* Read in the Excel file called `favourite-food.xlsx` from the `data-raw/` folder.

```{r label-me1, eval=FALSE}
fav_food <- read_excel("data-raw/favourite-food.xlsx")
fav_food
```

## Step 2: Clean the Data

* Clean up the missing data (`NA`s) and make sure you're happy with variable types. Modify the `read_excel` function to take care of these issues.

```{r label-me2, eval=FALSE}
fav_food <- read_excel("data-raw/favourite-food.xlsx", 
                       col_names = c("ID", "fullname", "favfood", "mealplan", "age", "SES"),
                       na = c("N/A", "99999"))
fav_food

fav_food %>%
  mutate(age = case_when(
    fullname == "Chidiegwu Dunkel" ~ 5,
    TRUE ~ as.numeric(age)
  )) %>%
  summarize(mean_age = mean(age, na.rm = TRUE))
```

* Convert the SES (socioeconomic status) to a factor variables with levels in the 
following order: `Low`, `Middle`, `High`.

```{r label-me3}
SES <- factor(c("Low", "Middle", "High"))
SES
```

## Step 3: Save to CSV

* Write out the resulting data frame to `favourite-food.csv` in the `data/` folder.

```{r label-me4}
write_csv(fav_food, file = "data-raw/favourite-food.csv")
```

## Step 5: Verify CSV Data

* Finally, read `favourite-food.csv` back in from the `data/` folder and 
observe the variable types. Are they as you left them?

```{r label-me5}
fav_food_copy <- read_csv(file = "data-raw/favourite-food.csv")
fav_food_copy
```

# Part 2: Excel to RDS Workflow

## Step 1: Read the Data
* Similar to Part 1, read  the Excel file called `favourite-food.xlsx` from the `data-raw/` folder, and handle missing data and variable types.

```{r label-me6, eval=FALSE}
fav_food <- read_excel(___, ___)
fav_food 
```

## Step 2: Adjust Variable Types

* Convert SES (socioeconomic status) to a factor variables with levels in the 
following order: `Low`, `Middle`, `High`.

```{r label-me7}
# add code here
```

## Step 3: Save to RDS
* Write out the resulting data frame to `favourite-food.rds` in the `data/` folder.

```{r label-me8}
# add code here
```

* Read `favourite-food.rds` back in from the `data/` folder and observe the 
variable types. Are they as you left them?

```{r label-me9}
# add code here
```

## References {#references}
1. Assignment Adapted from [Mine Cetinkaya-Rundel's Data Science in a Box](https://github.com/rstudio-education/datascience-box)